---
title: 'Project 2: Telemarketing'
author: "Eric Jiang, Richard Shu, Mehreen Alavi, Christine Yan, Suki Jiang"
date: "3/22/2020"
output:
  html_document: 
    toc: yes
    theme: lumen
    highlight: tango
    code_folding: show
  word_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction 

Telemarketers will spend hours on the phone calling individuals to promote and sell a product or service to customers.  Most of the time, the telemarketers are met with many rejections from their clients, roughly 90% of the calls are unsuccessful.  In few cases, they actually succeed in selling their product or service.  Our team will be acting as consultants for a telemarketing firm to create a model to help solve the issue of profitability of call centers.  Each call made costs $1 to make and each successful call generates $6 in revenue for the firm. We will create a model composed of 3 different sub-models (Logistic Regression Model, KNN Model, and ANN Model), to predict, based on the variables, the liklihood of an individual subscribing to a campaign in order make the business profitable. If we can predict whether a customer is likely to buy or not, we can focus our tele-marketing efforts towards more willing buyers and save/make a ton of money.

The data set consists of 41188 data points separate into 22 variables.  Before we can work with the data, we needed to clean the data set.

#Loading and Data Cleaning
```{r, cache=TRUE, name="test"}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)

#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## NULLed Data

*Variables Nulled*

* X 
* duration

*Reason* 
For the sake of simplicity, we decided to remove the following variables as we did not find them to be integral for the analysis of our model.

## Factorized Data

*Variables Factorized*

* job
* marital
* education
* housing
* loan
* car
* contact
* month
* default
* day_of_week
* outcome
* y

*Reason*
We factored the following categorical variables because the data is represented as factors in R. Factors should be stored as a vector of integer values with a corresponding label to every unique integer. 

**Note all variables not listed above were left as is.**

## Getting Data Ready for Analysis

```{r, cache=TRUE, name="teleRead"}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into knn has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))
str(telemm)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
library(janitor)
tele_norm <- clean_names(tele_norm)
```


# Getting Train and Test Samples

```{r, cache=TRUE, name="trainData"}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, -match("yyes",names(tele_norm))]
tele_test <- tele_norm[test_set, -match("yyes",names(tele_norm))]
# 
#Now the response (aka Labels) - only the yyes column
tele_train_labels <- tele_norm[-test_set, "yyes"]
tele_test_labels <- tele_norm[test_set, "yyes"]
```

# Project start

# Load all libraries
```{r, cache=TRUE, name="libraries"}
library(gmodels)
library(class)
library(MLmetrics)
library(caret)
library(neuralnet)
```


# cost Profit Structure
```{r, cache=TRUE, name="cost"}
cost <- 1
revenue <- 6

success <- revenue - cost
fail <- - cost
```




# KNN Model

## Create plot to determine best K for KNN Model

```{r,cache=TRUE, name="findK"}
profit_vec <- c()

# Find most profitable k 
pb <- txtProgressBar(min = 1, max = 50, style = 3)
for (i in 1:50){
  KNNPred <- knn(tele_train, tele_test, as.factor(tele_train_labels), k=i)
  
  cmatrix_k <- confusionMatrix(as.factor(KNNPred), as.factor(tele_test_labels))
  
  profit_vec <- append(profit_vec, cmatrix_k$table[2,1] * fail + cmatrix_k$table[2,2] * success)
  
  setTxtProgressBar(pb, i)
}


```

## plot best k
```{r, cache=TRUE, name="plotK"}
# Used to find optimal K
# plot multiple on top of each other

plot(profit_vec, x=1:50, type = "l", col="red")
opt_k <- which.max(profit_vec)
# best k value
opt_k
# best profit
max(profit_vec)
```


## Build actual model with strong k
```{r, cache=TRUE, name="Kmodel"}
# run with optimal k

# not a model, straight into prediction
KNNPred <- knn(tele_train, tele_test, as.factor(tele_train_labels), k=opt_k)
cmatrix<- confusionMatrix(as.factor(KNNPred), as.factor(tele_test_labels))
cmatrix
# Profit
KNN_profit <- cmatrix$table[2,1] * fail + cmatrix$table[2,2] * success
KNN_profit

#subrate
KNN_subrate <- (cmatrix$table[2,2])/ sum(cmatrix$table[2,1], cmatrix$table[2,2])
KNN_subrate
```

## KNN Model Analysis
Based on the KNN model that we created, we were able to reach an accuracy of 88.24% accuracy in predicting the outcomes of our test data calls.  Based on the model, we are predicted to generate a profitability of $`r KNN_profit` if the call center were to reach out the customers that the model predicted would subscribe (only those that the model predicts to subscribe) to the campaign being promoted. This is calculated with the idea that each successful call generates $5 profit ($6 revenue with a $1 cost of call) and each failure call that we predicted would be successful is a net loss of $1. Based on our model, we would have a subscriber rate of 47.97% based on the people that we call.

# ANN Model

## Build ANN Model
```{r cache=TRUE, name="ANNModel"}

#Now add dependent variable back in
tele_train$yyes = tele_train_labels
tele_test$yyes = tele_test_labels
ANNModel <- neuralnet(tele_train_labels ~ ., hidden = c(10, 5), data = tele_train, stepmax = 1e8, lifesign = "full", threshold = 0.05)
plot(ANNModel)
```


## ANN Prediction Model
```{r, cache=TRUE, name="ANNPred"}
ANNPredict <- predict(ANNModel, tele_test, type = "response")


subscribe_test <- ifelse(ANNPredict < 0.50, 0, 1)

results <- data.frame(predict = subscribe_test, actual = tele_test$yyes)
CrossTable(subscribe_test, tele_test$yyes)

cm <- confusionMatrix(as.factor(results$predict), as.factor(results$actual))
# PROFIT
ANN_profit <- cm$table[2,1] * fail + cm$table[2,2] * success
ANN_profit
# SUBRATE OF PEOPLE THAT WE CALL
ANN_subrate <- (cm$table[2,2])/ sum(cm$table[2,1], cm$table[2,2])
ANN_subrate



```


## ANN Model Analysis
Based on the ANN model that we created, we were able to reach an accuracy of 89.42% accuracy in predicting the outcomes of our test data   Based on the model, we are predicted to generate a profitability of $`r ANN_profit` if the call center were to reach out the customers that the model predicted would subscribe (only those that the model predicts to subscribe) to the campaign being promoted. This is calculated using the true positives and true negative test cases in the confusion matrix. The subscriber rate that we got was 55.65%.

# Logistic Regression Model 

## Finding best GLM Model Threshold
```{r, cache=TRUE, name="findbestGLM"}

#Now add dependent variable back in
tele_train$yyes = tele_train_labels
tele_test$yyes = tele_test_labels

profit_vec <- c()

pb <- txtProgressBar(min = 0, max = 1, style = 3)
for (i in seq(from=0, to=1, by=0.01)){
  #make model
  log_model <- glm(yyes ~ ., data=tele_train, family = "binomial")
  #make prediction
  log_pred_test <- predict(log_model, tele_test, type="response")
  log_test <- ifelse(log_pred_test < i, 0, 1)
  
  cmatrix_t <- confusionMatrix(as.factor(log_test),as.factor(tele_test$yyes), positive = "1")
  profit_vec <- append(profit_vec, cmatrix_t$table[2,1] * fail + cmatrix_t$table[2,2] * success)
  
  setTxtProgressBar(pb, i)
}
```
## find best threshold
```{r, cache=TRUE, name="findOptThresh"}
# Used to find optimal K
# plot multiple on top of each other
# 0 to 20 is equivalent to 0 to 1 on intervals of 0.05
plot(profit_vec, col = "red")

opt_thresh <- (which.max(profit_vec) * 0.01)
# best threshold value
opt_thresh
# best profit
max(profit_vec)
```

## Build and test GLM Model
```{r, cache=TRUE, name="plotGLM"}
log_model <- glm(yyes ~ ., data=tele_train, family = "binomial")
summary(log_model)
log_pred_test <- predict(log_model, tele_test, type="response")
#can change 0.5 threshold
#Goal 16% of people subscribe
log_test <- ifelse(log_pred_test < opt_thresh, 0, 1)

CrossTable(as.factor(log_test),tele_test$yyes)
cm <- confusionMatrix(as.factor(log_test),as.factor(tele_test$yyes), positive = "1")
#glm confusion matrix
cm
# PROFIT
glm_profit <- cm$table[2,1] * fail + cm$table[2,2] * success
glm_profit
# SUBRATE OF PEOPLE THAT WE CALL
glm_subrate <- (cm$table[2,2])/ sum(cm$table[2,1], cm$table[2,2])
glm_subrate
```

## Logistic Model Analysis

Based on the logistic model that we created, we were able to reach an accuracy of 87.48% accuracy in predicting the outcomes of our test data calls.  Based on the model, we are predicted to generate a profitability of $`r glm_profit` if the call center were to reach out the customers that the model predicted would subscribe (only those that the model predicts to subscribe) to the campaign being promoted. This is calculated with the idea that each successful call generates $5 profit ($6 revenue with a $1 cost of call) and each failure call that we predicted would be successful is a net loss of $1. Based on our model, we would have a subscriber rate of 46.30% based on the people that we call.

# Combining all 3 Submodels to Make a Giant Model 

```{r, cache=TRUE, name="bigPred"}
#Add values of 0 and 1, if sum is greater than or equal to 2 then they are likely to subscirbe if sum is less than that then they are not likely to subscribe 
# post resample against tele test labels
# compare accuracy of indiv to the big model

# GLM: log_test
# ANN: ANNPredict
# KNN: KNNPred

big_pred <- cbind(log_test, KNNPred, ANNPredict)
big_pred <- as.data.frame(rowSums(big_pred))

big_pred <- ifelse(big_pred >= 2, 1, 0)
postResample(big_pred, tele_test_labels)
cm <- confusionMatrix(as.factor(big_pred),as.factor(tele_test$yyes), positive = "1")
combined_profit <- cm$table[2,1] * fail + cm$table[2,2] * success
# PROFIT
combined_profit
# SUBRATE OF PEOPLE THAT WE CALL
combined_subrate <- (cm$table[2,2])/ sum(cm$table[2,1], cm$table[2,2])
combined_subrate
```

# Conclusion

In order to find the overall sub-rate, we combined all the different types of test int one data frame. If the data point had at least 2 of the 3 models agreeing without our results, it would be set to true in our big prediction model. After re-sampling, we came up with a combined sub-rate of 43.70% and a profit of 2431. Overall, This suggest that using all our models together, we can find the most likely candidates to sign up while wasting as little time as possible on rejections. 

Our group has achieved our goal of creating a model that is adequate enough in creating a model that, if used, will help the telemarketing firm profitable with a subscribe rate of 43.70%. The KNN Model would generate a profitability of $1247 with a subscriber rate of 48.11%, ANN model would generate a profit of $1139 with a subscriber rate of 55.65%, and the logistic model would generate a profit of $2477 and a subscriber rate of 46.30%.  

Looking at all of our models and the combined model.  We would have the highest subscriber rating if we were to only use the ANN model compared to the other models. The model that would generate the greatest profitability based on our test data however would be the logistic model.  


